### 2020-12-22 msc-thesis.tex
Changed structure and added info about ozg basic use case

\subsection{Administrative Service}
Unemployment benefit (Arbeitslosengeld II: AGII) is selected as an example for a digitized administrative service, because it has a high priority according to the "OZG-Informationsplattform" and is well documented.

The AGII is accessible through the "one for all" method through the administration portal of the federal republic. The digitalization of the service was done by the member state Nordrhein-Westfalen. The purpose of this service is to enable application for unemployment benefit and the result is an approval or denial by the responsible institution of the commune. The digitized process of this service enhances it to be manageable on an administration portal trough a user profile in the following way:

In order to access the service, a user must authenticate for an existing user profile or create one.

@@

\subsubsection{System Components}
The system architecture consists of the following system components where each component is responsible for processing a certain group of tasks:

@@

\chapter{Problem Analysis}

@@

\subsection{User Requirements}

\subsection{OZG Requirements}

The information platform of the OZG contains information about many administration services in form of process diagrams \cite{BMI:Ergebnisse}. They serve as a resource to identify important OZG scenarios of administration processes. The following scenarios were identified:

\subsubsection{Identity Management}

\textbf{Scenario Profile Management}
\begin{itemize}
    \item Create a user profile
    \item Delete a user profile
    \item Check existence of a user profile
\end{itemize}

\textbf{Scenario Identity verification}
\begin{itemize}
    \item Login to a user profile
    \item Provide multiple levels of security for identity verification
    \item Usage of a guest profile
\end{itemize}

\subsubsection{Request Management}

\textbf{Scenario Request Preparation}
\begin{itemize}
    \item Search for administration services
    \item Check necessity of a profile
    \item Check required level of identity verification
    \item Selection of institution responsible for processing the request (Specification of current location)
\end{itemize}

\textbf{Scenario Request Creation}
\begin{itemize}
    \item Filling in a form for an application
    \item Automated filling in of form with saved personal data
    \item Collaboration on application by multiple identities
\end{itemize}

\textbf{Scenario Request Delivery}
\begin{itemize}
    \item Transmission of an application to responsible institution
\end{itemize}

\textbf{Scenario Request Processing}
\begin{itemize}
    \item Period of validity of applications
    \item Notification of user about missing information or documents
    \item Transmission of missing information
    \item Notification of user about required preliminary administration services
    \item Communication through E-Mail
    \item Cancel an application
    \item Approvals of user to e.g. data protection or information transfer
    \item Modification request of application after transmission
    \item Notification of received application by institution
    \item Request status update by user
    \item Sending notification to confirm the reading of a message
    \item Notification of certain events to separate person e.g. parents
    \item Request of institution about explicit document
\end{itemize}

\textbf{Scenario Request Finalization}
\begin{itemize}
    \item Notification of outcome of process / application
    \item Objection of user to result of the process
    \item Access to signed digital formula of result of process
    \item Definition of dates for evens
\end{itemize}

\subsubsection{Data Management}

\textbf{Scenario Access Management}
\begin{itemize}
    \item Access to an application by multiple separate identities
    \item Sharing of documents saved in a wallet
\end{itemize}

\textbf{Scenario Data Consistency}
\begin{itemize}
    \item Period of validity of documents
    \item Profile data discrepancies between involved user profiles
\end{itemize}

\textbf{Scenario Data Accessibility}
\begin{itemize}
    \item Upload of e.g. documents and certificates
    \item Saving personal data entered in a form to the user profile
    \item Protocol of all processes accessible with information about interactions
\end{itemize}

\section{Solution with IMP}

\section{Integration Challenges}
The following challenges are a result of the functionalities an IMP system provides in addition to conventional identity management systems. The origin of the challenges is the interoperability of the IMP identity with multiple SPs. It is the purpose of the integration architecture to solve as many of these challenges as possible.

@@

\chapter{Integration Proposal}
The bachelor thesis proposes an integration using a connector because:

\section{IMP System}
List of functionalities of the IMP System based on research and analysis of the OZG scenarios:

\section{IMP Connector}
Interfaces of the connector for usage by the integration architecture:

\section{Basic Integration Architecture}

\subsection{Version 1}

\subsubsection{Requirements}

\subsubsection{Flow Diagrams}

\includegraphics[width=15cm]{Basic Integration Onboarding.png}

\includegraphics[width=15cm]{Basic Integration Application.png}

\subsubsection{Messaging Architecture}

\subsection{Version 2}

\subsubsection{Requirements}

\subsubsection{Flow Diagrams}

\subsubsection{Messaging Architecture}

@@

\chapter{Outlook}

\section{Advanced Integration Architecture}

>>>>

\subsection{Basic Use Case}
The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}. Each process consists of multiple sub-processes. When comparing the processes, one can see, that some sub-processes occur very often and in similar arrangements. Those arrangements can be called the basic use case of OZG services.

The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:

\paragraph{1. Selection of Application Form}
The user visits any administration portal of the portal network and types a search term in the corresponding search field. The user is then presented with a list of search results consisting of administrative services. If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service. This page provides information about the administration service along with instructions on how to access the form for application. The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.

\paragraph{2. Login to User Profile}
Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal. The user has to finish authentication steps, which can consist for example of a username and password. Depending on the authentication method, a trust level of the current session is determined. With approval from the user, personal information from his profile is provided towards the form-server.

\paragraph{3. Filling in of Application}
Personal information from the user profile is used to by the form-server to fill as many fields of the form as possible. The form with prefilled information is then presented to the user. The interactive form can then be modified by the user. Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.

\paragraph{4. Uploading Attachments}
The user can upload documents to his user profile and reference them from the form.

\paragraph{5. Submission of Application}
The user again authenticates for his user profile and authorises the form-server to submit the application. The form-server saves the application until he is notified to delete it. The form-server submits the application to the administration portal which hosts the administrative service.

\paragraph{6. Reception of Application by Administration Portal}
The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.

\paragraph{7. Submission of Application to Data-Exchange Platform}
The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.

\paragraph{8. Sending of Acknowledgment}
The data-exchange platform notifies the user through the inbox functionality of the user profile if the application was submitted successfully.

@@

\subsubsection{System Components}
The system architecture consists of the following system components where each component is responsible for providing a certain set of services:

@@

\chapter{Identity Management}

@@

\subsection{User Perspective}

\subsection{OZG Perspective}

\section{IMP Solution Proposal}

\chapter{IMP Integration Architecture}

\subsection{Integration Challenges}

The following challenges are a result of the functionalities an IMP system provides in addition to conventional identity management systems. The origin of the challenges is the interoperability of the IMP identity with multiple SPs. It is the purpose of the integration architecture to solve as many of these challenges as possible.

@@

\subsection{Basic Use Case}

\subsection{Extensions}

\section{Integration Proposal}

\subsection{IMP Connector}

\subsection{Messaging}

\section{Basic Use Case}

\subsection{Process Integration}

\subsection{Messaging Integration}

\section{Extension: Inbox}

\section{Extension: Collaboration}

@@

\chapter{Outlook: Advanced IMP Integration}
